A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Explain refs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1002 43ef1190-90fd-4dd7-a769-d0121f02b80e

The implications of HTTP for query caches has been discussed by
\cite{kaseicache}. In \cite{sparqlproxy} the authors implemented a
reverse proxy that controlled the changes to the dataset, and
therefore could make sure the proxy had all the information needed to
determine freshness. We are interested in the situation where the
changes cannot be controlled.

A general caching approach is given in \cite{yang2011caching}\todo{explain} . In
\cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries\todo{explain} .

>>>>

The implications of HTTP for query caches has been discussed by
\cite{kaseicache}, where it is shown how changes can be tracked
efficiently using different data structures. In \cite{sparqlproxy} the
authors implemented a reverse proxy that controlled the changes to the
dataset, and therefore could make sure the proxy had all the
information needed to determine freshness. We are interested in the
situation where the changes cannot be controlled.

In \cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries.
